---
title: "Algoritmos en Bioinformática Estructural"
date: "`r format(Sys.time(), '%d %B %Y')`"
author:
- affiliation: Estación Experimental de Aula Dei-CSIC, Zaragoza, España, https://eead.csic.es/compbio
  name: Bruno Contreras Moreira
output:
  bookdown::gitbook: 
    split_by: none
documentclass: book
bibliography: bib_myarticles_md.bib
link-citations: yes
---


<!-- TODO
https://stackoverflow.com/questions/41376989/how-to-include-google-analytics-in-an-rmarkdown-generated-github-page
-->



```{r, child='README.md'}
```

<!--
```{perl, highlight=TRUE, eval=FALSE, }
#!/usr/bin/perl -w

# prog1.1 
# Bruno Contreras-Moreira
# Nearest Neighbor dG calculator

use strict;

# global variables
my $T           = 37; # temperature(C)
my $windowL     = 15;  # window length, http://www.biomedcentral.com/1471-2105/6/1
```
-->


<!-- importa capítulos originales .tex convertidos a .md  -->

```{r, child='fixmerge.md'}
```

<!--
%\chapter{Alphafold} \label{AF}
%\input{alphafold.tex} 
-->

# Apéndices

## Abreviaturas {#tab:abbrev}

|||
|:---|:----------------------------|
|CASP|Critical Assessment of Techniques for Protein Structure Prediction|
|CATH|Protein Structure Classification database|
|CM|Comparative Modelling|
|DSSP|Define Secondary Structure of Proteins|
|FR|Fold Recognition|
|NMR|Nuclear Magnetic Resonance|
|NN|Nearest Neighbor|
|PCR|Polymerase Chain Reaction|
|PDB|Protein data Bank|
|SCOP|Structural Classification of Proteins|
|TF|Transcription Factor|
|SS|Secondary Structure|


<!--\section{Muestra de R \italics{Markdown} para tus trabajos} \label{md}
\verbatiminput{sample_markdown.Rmd}-->



# Bibliografía

